A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
Introduction changes

In this \paper\ we present a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.

@@

...we are not the first to search the \KT\ data (cite Crossfield, etc),
and we build on ideas from \kepler\ searches (cite Petigura and
\kepler).

...our goals are to find new exoplanets, to generate targets for
ground-based and space-based (JWST, even) follow-up, and to understand
the full population of exoplanets.  We (as a community) have made
progress on all these fronts, but there is much more to do.

...The future is \tess\ (cite something); everything we do here is
highly relevant to that important mission!

\section{Photometry}

@@

\section{Joint transit \& variability model}

@@

\section{Search pipeline}

>>>>

In this \paper\ we present a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.
We assume the trends in the observed light curves in each star due to 
spacecraft motion are shared by each star, and run PCA to measure the dominant
modes.
We then search for planets by modeling the data as a linear combination of
these basis vectors and a transit model.
Such a technique builds on the ideas of previous PCA-based \kepler\ planet 
searches, such as those of (cite-Petigura).

The methods developed within this paper are highly relevant to the upcoming 
\tess\ mission (Cite-Ricker 14). 
\tess will feature pointing precision of \sim 3 arcseconds (cite), 
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

Catalogs of transiting planets found by \KT\ will be important to better 
understand the formation and evolution of planetary systems. 
These planets, especially when they orbit especially bright or late-type stars,
will be useful targets for ground-based and space-based follow-up, both for 
current facilities and those planned in the near-future such as JWST.

The \paper\ is organized as follows. 
In \textsection\ref{sec:phot}, we describe our analysis of the photometric 
data collected by \KT.
In \textsection\ref{sec:model}, we expain our simultaneous fit of the 
systematics and transit model.
In \textsection\ref{sec:search}, we describe our search pipeline for 
planet candidates.
In \textsection\ref{sec:perform}, we quantify the performace of our pipeline 
through the analysis of injected planetary signals.
In \textsection\ref{sec:K2OIs}, we present the results of our search: 
catalogs of \KT\ planet candidates and eclipsing binaries.
In \textsection\ref{sec:discuss}, we discuss our results and outline our
future work.

@@

\section{Photometry}
\label{sec:phot}

@@

\section{Joint transit \& variability model}
\label{sec:model}

@@

\section{Search pipeline}
\label{sec:search}
